This dissertation first contributes our geometric-based planning algorithm
for robots to describe and reason about
uncertainty, termed the ``constrained geometric approximation approach.''

Previous work produced computationally expensive methods to represent a robot's
knowledge of its states and uncertainty explicitly, using a state in
an information space. 
%
In contrast, our approach is computationally inexpensive based
specifically on an approximation method using simple geometric data structures 
that are suitable for robots 
having major limitations in both sensing and computation. 
%
We provide simulations of sensor-based navigation
tasks, along with experimental results.
%
We conclude that using our results a robot can achieve similar success rate at a small fraction of the computational cost
by maintaining simple representations of the incomplete information.
  
The dissertation also contributes two decentralized algorithms for the multi-robot
lattice pattern formation problem. 
% 

Prior work solved such problems by constituting only particular lattice patterns.
%
Our two formation algorithms enable robots to form arbitrary lattice patterns without global knowledge of the system.
%
Both of the formation algorithms feature in representing the lattice as
a directed graph, in which edges show the desired rigid body transformations
between the robot and the its neighbors. 
%
Another common feature of the two algorithms is that robots organize themselves using tree structures. 

The first formation algorithm enables each robot to perform distributed task assignment using
only local information.
%
The experimental results demonstrate that the algorithm executes efficiently and 
scales reasonably well as the number of robots increases.
Moreover, the algorithm is stateless and is robust to system failures.

We analyze the pitfalls of the proposed task-assignment-based formation algorithm.
%With regard to the limitations of the first algorithm, 
Based on the analysis, we have designed another formation algorithm that has new features including:
the bounded execution time, a novel motion strategy that guarantees the network connectivity, 
and the improved final lattice formation quality.
%
Furthermore, we have proved the correctness of the new algorithm and 
conducted groups of experiments to compare the timing performance 
and the formation qualities of both formation algorithms.
